---
pagetitle: "Trafford Digital Services"
lang: "en-GB"
output: 
  html_document:
    css: styles.css
    highlight: null
    mathjax: null
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(crosstalk) ; library(tidyverse) ; library(sf) ; library(leaflet) ; library(leaflet.extras) ; library(reactable) ; library(shiny) ; library(htmlwidgets) ; library(htmltools)

# local authority boundary
sf <- st_read("data/local_authority.geojson", quiet = TRUE)

# places
df <- read_csv("data/digital_skills_services.csv") %>%
  mutate(Category = fct_relevel(as_factor(Category),
                             level = c("Community hub", "Library", "Charity/community group", "Education establishment", "Training provider", "Retailer", "Job Centre", "Digital Bootcamp provider")),
         `Target audience` = fct_relevel(as_factor(`Target audience`),
                             level = c("Everyone", "Adults aged 19 +", "Adults and young people with disabilities", "Customers", "Families", "Individuals with hearing impairment", "Jobseekers", "Older people", "Residents", "Students", "Women", "Young people")),
         popup = str_c("<strong>", `Organisation name`, "</strong><br/>",
                        ifelse(is.na(Phone),"",str_c("Tel: ", Phone, "<br/>")), 
                        ifelse(is.na(Email),"",str_c("Email: ", Email, "<br/>")), 
                        ifelse(is.na(Website),"",str_c("<a href='", Website, "'target='_blank'>Website</a><br/><br/>")),
                        ifelse(is.na(Address),"",str_c("Address: ", Address, ", ", Postcode))
                       ) %>% map(HTML))

# shared dataframe
sd <- SharedData$new(df, group = "Organisation name")
# subset of shared dataframe
sd_table <- select(df, `Organisation name`, `Additional information`) %>%
  SharedData$new(group = "Organisation name")
```

```{r, map}
map <- leaflet(sd, width = "100%", height = 600) %>%
  addTiles(urlTemplate = "https://{s}.basemaps.cartocdn.com/light_all/{z}/{x}/{y}{r}.png", attribution = '&copy; <a href="https://www.openstreetmap.org/copyright">OpenStreetMap</a> contributors &copy; <a href="https://carto.com/attributions">CARTO</a> | <a href="https://www.ons.gov.uk/methodology/geography/licences">Contains OS data © Crown copyright and database right (2021)</a>', options = tileOptions(minZoom = 6, maxZoom = 18)) %>%
  setView(lng = -2.330256, lat= 53.421829, zoom = 11.5) %>%
  addPolygons(data = sf, fillColor = "#CCCCCC", weight = 0.8, opacity = 1, color = "#212121") %>%  
  addAwesomeMarkers(popup = df$popup, icon = ~makeAwesomeIcon(icon = "fas fa-hand-pointer", library = "fa", iconColor = "#FFFFFF", markerColor = "blue")) %>%
  addFullscreenControl()
```

```{r, table}
# improve accessibility
options(reactable.language = reactableLang(
  noData = "No organisations found",
  pagePreviousLabel = "Previous page",
  pageNextLabel = "Next page"))

table <- reactable(
  sd_table,
  resizable = TRUE,
  borderless = FALSE,
  compact = FALSE,
  wrap = TRUE,
  searchable = TRUE,
  highlight = TRUE,
  selection = "multiple",
  onClick = "select",
  rowStyle = list(cursor = "pointer"),
  columns = list(
     `Organisation name` = colDef(maxWidth = 300,
                                  style = list(position = "sticky", left = 0),
                                  headerStyle = list(position = "sticky", left = 0))
    )
)
```
<header>
```{r, logo}
a(
  href = "https://www.trafford.gov.uk",
  target = "_blank",
  img(src = "https://www.trafforddatalab.io/images/trafford_council_logo_black_on_white_100px.png", 
      alt = "Trafford Council", 
      width = "70",
      style = "position:absolute; top:0; right:0; padding: 5px;")
  )
```
</header><main>
```{r, ui}
div(class = "container-fluid",
    h1("Trafford Digital Services", style = "padding-top: 25px; margin-bottom: 20px;"),
    p("Discover the range of digital support available in Trafford. Find details of Wi-Fi hotspots, computer access and device lending schemes, along with contact information and website links to local organisations."),
    br(),
    div(class = "row",
        div(class = "col-xs-12 col-sm-6 col-md-8 col-lg-8", map),
        div(class = "col-xs-6 col-sm-3 col-md-2 col-lg-2", 
            list(
              # Category
              filter_checkbox(id = "category", label = "Category", sharedData = sd, group = ~Category),
              br(),
              # `Target audience`
              filter_checkbox(id = "Target audience", label = "Target audience", sharedData = sd, group = ~`Target audience`),
              br()
            )),
        div(class = "col-xs-6 col-sm-3 col-md-2 col-lg-2", 
            list(
              # WiFi
              filter_checkbox(id = "WiFi", label = "WiFi", sharedData = sd, group = ~ifelse(WiFi == "x", "Available", NA), inline = TRUE),
              br(),
              # Computers
              filter_checkbox(id = "Computers", label = "Computers", sharedData = sd, group = ~ifelse(Computers == "x", "Available", NA), inline = TRUE),
              br(),
              # Device lending
              filter_checkbox(id = "Device lending", label = "Device lending", sharedData = sd, group = ~ifelse(`Device lending` == "x", "Available", NA), inline = TRUE),
              br(),
              # Training and/or support
              filter_checkbox(id = "Training and/or support", label = "Training and/or support", sharedData = sd, group = ~ifelse(`Training and/or support` == "x", "Available", NA), inline = TRUE),
              br(),
              # Essential Digital Skills (up to Level 2)
              filter_checkbox(id = "Essential Digital Skills (up to Level 2)", label = "Essential Digital Skills (up to Level 2)", sharedData = sd, group = ~ifelse(`Essential Digital Skills (up to Level 2)` == "x", "Available", NA), inline = TRUE)
            ))),
    br(),
    h2("Additional information"),
    div(class = "row",
        div(class = "col-sm-12", table)),
    div(class = "row",
        div(class = "col-sm-12", 
            p("There are a lot of other locations across the borough that you are able to access free WiFi. A range of retailers offer these services to paying customers. If you have WiFi at home your provider might also offer free WiFi hotspots while you’re out and about."),
            p("Some examples of organisations that offer WiFi to customers while on their premises are Aldi, McDonalds and Costa Coffee but there are many more. All you need to do is look out for the Free WiFi symbol once you are inside which might look something like this:"),
            img(src = "images/wifi_logo.jpg"),
            img(src = "images/wifi_logo2.png"),
            br(), br(), br()
        )
    ))
```
</main>
<script>
  // Remove the crosstalk selection button from the Leaflet map. Map may not have initialised at this point so set up an interval to keep calling until it has
  var removeSelectionButtonFn = setInterval(removeSelectionButton, 100);
  
  function removeSelectionButton() {
    try {
      // We don't have an id or name so have to do it by classname and then check we have the correct button by testing the 'title' attribute
      var arrEasyButtonContainer = document.getElementsByClassName('easy-button-container');
  
      for (var i = 0; i < arrEasyButtonContainer.length; i++) {
        if (arrEasyButtonContainer[i].childNodes[0].title == "Make a selection") {
          var parent = arrEasyButtonContainer[i].parentNode;
          parent.removeChild(arrEasyButtonContainer[i]);    // remove the whole container plus button
          clearInterval(removeSelectionButtonFn);  // cancel any further calls to this function as we have completed all actions
        }
      }
    }
    catch(e) {
      clearInterval(removeSelectionButtonFn);   // something went wrong so cancel fn call
    }
  }
  
  
  // Add aria-label attribute to the fullscreen Leaflet map button to identify its purpose as the link is empty (assessibility issue)
  // Map may not have initialised at this point so set up an interval to keep calling until it has
  var updateFullscreenButtonFn = setInterval(updateFullscreenButton, 100);
  
  function updateFullscreenButton() {
    try {
      // We don't have an id or name so have to do it by classname
      var arrFullscreenButtonLink = document.getElementsByClassName('leaflet-control-fullscreen-button');
      
      if (arrFullscreenButtonLink.length > 0) {
        // set aria-label to describe the function of the link/button
        arrFullscreenButtonLink[0].setAttribute('aria-label', 'Maximise/minimise map.');
        
        clearInterval(updateFullscreenButtonFn);    // cancel any further calls to this function as we have completed all actions
      }
    }
    catch(e) {
      clearInterval(updateFullscreenButtonFn);    // something went wrong so cancel fn call
    }
  }
  
  
  // Add type="hidden" attribute to all form elements with classname "irs-hidden-input" to remove errors in
  // WAVE due to the inputs not having labels.
  // The controls may not have initialised at this point so set up an interval to keep calling until they have
  var addInputHiddenFn = setInterval(addInputHidden, 500);
  
  function addInputHidden() {
    try {
      var arrHiddenInputs = document.getElementsByClassName('irs-hidden-input');
    
      if (arrHiddenInputs.length > 0) {
        for (var i = 0; i < arrHiddenInputs.length; i++) {
          arrHiddenInputs[i].setAttribute('type', 'hidden');
        }
        
        clearInterval(addInputHiddenFn);   // cancel any further calls to this function as we have completed all actions
      }
    }
    catch(e) {
      clearInterval(addInputHiddenFn);   // something went wrong so cancel fn call
    }
  }
  
  
  // Remove label tags created by crosstalk for the checkboxes and sliders as they cause validation errors,
  // and replace them with fieldsets and legends containing the text of the label
  // Reason for the error is that the 'for' attribute isn't referencing an id of a form control
  // NOTE: the do while loop always references array index 0 because as the elements are removed from the DOM they are also removed from the array
  var arrFormLabels = document.getElementsByClassName('control-label');
  var parent;
  var labelText;
  var newNode;
  var fieldset;
  var legend;
  
  do {
    parent = arrFormLabels[0].parentNode;                   // container of the label
    labelText = arrFormLabels[0].firstChild.textContent;    // get the label text we want to preserve
    
    // create the new fieldset and legend nodes first
    legend = document.createElement('legend');
    legend.appendChild(document.createTextNode(labelText));
    legend.setAttribute('class', 'formGroupHeading');
    fieldset = document.createElement('fieldset');
    fieldset.appendChild(legend);
    
    parent.removeChild(arrFormLabels[0]);   // remove the old label
    
    // Now add all the children of parent to the newly created fieldset
    while (parent.childNodes.length > 0) {
      fieldset.appendChild(parent.childNodes[0]);
    }
    
    parent.appendChild(fieldset);    // add the fieldset to the parent
    
    // For the slider widgets we also need to add an aria-label to describe the purpose of the group
    if (parent.classList.contains('crosstalk-input-slider')) {
      parent.setAttribute('aria-label', 'Slider range control for ' + labelText);
      parent.setAttribute('tabindex', '0');    // allow the slider group to be accessed via tab
    }
  }
  while (arrFormLabels.length > 0);
  
  
  // Add aria-labels to the slider components
  // The inner controls may not have initialised at this point so set up an interval to keep calling until they have
  var slidersFn = setInterval(sliders, 500);
  
  function sliders() {
    try {
      var arrSliders = document.getElementsByClassName('crosstalk-input-slider');   // The div surrounding the control group
    
      var arrMinValues = document.getElementsByClassName('irs-min');          // range min label
      var arrMaxValues = document.getElementsByClassName('irs-max');          // range max label
      var arrFromValues = document.getElementsByClassName('irs-from');        // range from label
      var arrToValues = document.getElementsByClassName('irs-to');            // range to label
      var arrSingleValues = document.getElementsByClassName('irs-single');    // range from - to label
      var arrSliderHandles = document.getElementsByClassName('irs-slider');   // the handles on the sliders
      
      if (arrFromValues.length == arrSliders.length) {
        // We know how many sliders there are on the page as their containers are written into the HTML.
        // The actual slider widgets are dynamically created within them at runtime.
        // If the array lengths match we know that the widgets have all been created
        for (var i = 0; i < arrSliders.length; i++) {
          arrMinValues[i].setAttribute('aria-label', 'Minimum range value');
          arrMaxValues[i].setAttribute('aria-label', 'Maximum range value');
          arrFromValues[i].setAttribute('aria-label', 'Lower range value');
          arrToValues[i].setAttribute('aria-label', 'Upper range value');
          arrSingleValues[i].setAttribute('aria-label', 'Range values');
        }
        
        // these are the slider handles
        for (var i = 0; i < arrSliderHandles.length; i++) {
          arrSliderHandles[i].setAttribute('aria-label', 'slider handle');    // not using role="slider" as unfortunately this control doesn't seem to conform to the WAI-ARIA specification for the slider role
        }
        
        clearInterval(slidersFn);   // cancel any further calls to this function as we have completed all actions
      }
    }
    catch(e) {
      clearInterval(slidersFn);   // something went wrong so cancel fn call
    }
  }
</script>