---
output: html_document
---

<link rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/font-awesome/4.7.0/css/font-awesome.min.css">

<style>
@import url('https://fonts.googleapis.com/css?family=Roboto');

body 
{
    font-family: 'Roboto', sans-serif;
    color: #757575;
}

h1, h2, h3, h4, h5, h6, strong
{
    color: #fc6721;
}

a
{
    color: #fc6721;
    text-decoration: none;
}

a:hover
{
    text-decoration: underline;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(crosstalk) ; library(shiny) ; library(tidyverse) ; library(sf) ; library(leaflet) ; library(DT) ; library(summarywidget) ; library(plotly)

bdy <- st_read("https://www.traffordDataLab.io/spatial_data/local_authority/2016/gm_local_authority_super_generalised.geojson", quiet = TRUE) %>% 
  filter(area_name == "Trafford")
df <- read_csv("https://www.traffordDataLab.io/open_data/road_casualties/2017/STATS19_casualty_data_2017.csv") %>% 
  filter(area_name == "Trafford") %>% 
  mutate(month = factor(month, levels = month.abb),
         ageband = factor(ageband, levels=c("0-5","6-10","11-15","16-20","21-25","26-35","36-45","46-55","56-65","66-75","Over 75"), ordered = TRUE)) %>% 
    select(-easting, -northing)
sd <- SharedData$new(df)
```

<a href='https://trafforddatalab.github.io' target='_blank'><img src='https://trafforddatalab.github.io/assets/logo/trafforddatalab_logo.svg' style='height: 33px; border: 0; float: left;' alt='Trafford Data Lab' border='0'></a>
<h3 style="text-align: right;">Reported road casualties in Trafford</h3></br>


```{r}
bscols(widths = c(4,NA),
  list(
    tags$style(HTML('.js-irs-0 .irs-single, .js-irs-0 .irs-bar- edge, .js-irs-0 .irs-bar {
background: #fc6721; border-top: 1px solid #fc6721; border-bottom: 1px solid #fc6721 ;}
.irs-from, .irs-to, .irs-single { background: #757575 }')),
    filter_slider(id = "date", label = "Date range", sharedData = sd, column = ~date,
                  step = 1, round = TRUE, sep = "", ticks = FALSE),
    filter_checkbox(id = "mode", label = "Mode of travel", sharedData = sd, group = ~mode, inline = FALSE, columns = 2),
    filter_checkbox(id = "severity", label = "Casualty severity", sharedData = sd, group = ~severity, inline = FALSE, columns = 3)
    ),
  leaflet(sd, height = 300) %>% 
    addProviderTiles(providers$CartoDB.Positron) %>% 
    addPolylines(data = bdy, stroke = TRUE, weight = 3, color = "#757575", opacity = 1) %>% 
    addCircleMarkers(stroke = TRUE, weight = 1, color = "#000000", 
                     fillColor = ifelse(
                       test = df$severity == "Slight",
                       yes = "#ccebc5",
                       no = ifelse(
                         test = df$severity == "Serious",
                         yes = "#b3cde3",
                         no = "#fbb4ae")), 
                     fillOpacity = 0.8,
                     radius = 8, 
                     popup = ~df$text) %>% 
    addLegend(position = "bottomleft", colors = c("#fbb4ae", "#b3cde3", "#ccebc5"),
              labels = c("Fatal", "Serious", "Slight"), opacity = 0.8, title = NULL)
  )
```
<p style="font-size: large; text-align: center;">There were **`r summarywidget(sd, digits = 0)`** road casualties reported in Trafford. Of these, **`r summarywidget(sd, selection = ~sex == "Female", digits = 0)`** were female and **`r summarywidget(sd, selection = ~sex == "Male", digits = 0)`** were male.</p></br>

```{r}
bscols(widths = c(4, 4, 4),
plot_ly(sd, x = ~factor(month), height = 300) %>%
    add_histogram(color = I("#bdbdbd")) %>%
     layout(title = "Month",
            xaxis = list(title = "", fixedrange = TRUE),
            yaxis = list(title = "", tickformat = ',d', fixedrange = TRUE),
            hoverlabel = list(bgcolor = "#757575")) %>%
  highlight(color = "#fc6721", on = "plotly_click") %>% 
  config(displayModeBar = F),
plot_ly(sd, x = ~factor(hour), height = 300) %>%
    add_histogram(color = I("#bdbdbd")) %>%
     layout(title = "Hour",
            xaxis = list(title = "", range = c(0, 23), fixedrange = TRUE),
            yaxis = list(title = "", tickformat = ',d', fixedrange = TRUE),
            hoverlabel = list(bgcolor = "#757575")) %>%
  highlight(color = "#fc6721", on = "plotly_click") %>% 
  config(displayModeBar = F),
plot_ly(sd, x = ~factor(ageband), height = 300) %>%
    add_histogram(color = I("#bdbdbd")) %>%
     layout(title = "Age group",
            xaxis = list(title = "", fixedrange = TRUE),
            yaxis = list(title = "", tickformat = ',d', fixedrange = TRUE),
            hoverlabel = list(bgcolor = "#757575")) %>%
  highlight(color = "#fc6721", on = "plotly_click") %>% 
  config(displayModeBar = F)
)
```

```{r}
DT::datatable(sd, extensions = "Scroller", style = "bootstrap", class = "compact", width = "100%", rownames = FALSE,
          options = list(dom = 't', deferRender = TRUE, scrollX = TRUE, scrollY = 220, scroller = TRUE,
                         initComplete = JS(
                           "function(settings, json) {",
                           "$(this.api().table().header()).css({'background-color': '#F8F8F8', 'color': '#000'});",
                           "}"),
                         columnDefs = list(list(visible = FALSE, targets = c(2:3, 10:13)))),
          colnames = c(
            "Id" = "AREFNO",
            "Date" = "date",
            "Hour" = "hour",
            "Mode" = "mode",
            "Severity" = "severity",
            "Light conditions" = "light",
            "Sex" = "sex",
            "Age band" = "ageband")
          )
```

<a href="https://github.com/traffordDataLab/maps/tree/master/road_casualties" target="_blank">
		<i class="fa fa-github" style="font-size:24px; float:right;"></i>
</a>

